---
title: "Introduction to scoreBPQ"
author: "Original R code by Logan Holmes. Package and Vignette created by Evan Nix. Based on Psychometric Research by Jacek Kolacz."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{scoreBPQ-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



The scoreBPQ package makes scoring the Body Perception Questionnaire fast and easy, but some initial checks must be made to ensure that the data is formatted properly.

* In order for the scoring function to work properly, data must be in the proper form:
    * All bpq items have the prefix "bpq_"
    * All bpq items must be properly numbered, from 1 to total number of items. 
      * Common Error: numbering each subscale separately. This will break the code.
    * The correct form must be set as an argument in the function call (Default: Short Form)
    
For detailed descriptions of item numbers for each form, see Page 14 of the BPQ Manual: https://static1.squarespace.com/static/5c1d025fb27e390a78569537/t/5ccd9de46e9a7f37d527bbc9/1556979173189/BPQ_Information_and_Scoring_v2_091518.pdf

---

# Example Use

## Installation
```{r, warning = F, message = F}
devtools::install_github("ejnix/scoreBPQ")
```



```{r setup}
library(scoreBPQ)
```

## Data: test_data
An example dataset has been included in the package as a reference for what properly formatted raw data should look like. This dataset is documented in ?test_data. We can view this dataset at any time by calling test_data in the R console.
```{r}
test_data
```


test_data is an example of the BPQ short form, which contains 46 items. 

## BPQ_all_scoring

The scoreBPQ package contains several functions, but they are structured in a way to interact with each other behind the scenes. Once you have formatted your data, all you need to use is the function **BPQ_all_scoring**. This function will do all the work in the background and output a scored dataframe.

---

In order to score test_data, all we need to do is call the function BPQ_all_scoring. 

* The first argument: df, is the input dataframe, 
* The second argument: form, is the form of the Body Perception Questionnaire, 
    * More information on how to use different forms can be found in the documentation ?BPQ_all_scoring
* The third argument: version, is the population norms that the data will be compared to. Population norms were collected in 2018 and 2020. It is advised to use version = 2020 for all new data, but certain users will want to compare to the older norms, perhaps if their study took place in 2018.
```{r}

# Outputs original dataframe, with scored subscales appended to the end of the dataframe.
BPQ_all_scoring(df = test_data, form = "SF", version = 2020)


```

In the output, you will find all scored subscales, and the percent of missing data for each subscale appended to the end of the input dataframe.


## Common Errors
### Incorrect column names
A common error is a mistake in the column names of the bpq items. To simulate this, we will create a new dataframe, test_data_incorrect, by renaming all the prefixes from 'bpq' to 'body_perception'.
```{r results='hide'}
library(tidyverse)
```


```{r}
test_data_incorrect <- test_data %>% 
  rename_all(~gsub("bpq", "body_perception", .))
```


```{r, error=T, purl=F}
BPQ_all_scoring(test_data_incorrect)
```


### Calling the wrong functions
As previously stated, there are several functions included in the package. These can be used to score individual responses, but if given an entire dataset of multiple responses, they will break.
```{r, error=T, purl=F}
BPQ_single_scoring(test_data)
```

Remember to always use the function BPQ_all_scoring when scoring multiple observations.


### Using non-numeric data
Another common error is to input the character string responses instead of their numeric conversions. To simulate this, we will create a new dataframe, test_data_character, by changing all the numbers back to their character string analogues.
```{r}
test_data_character <- test_data %>% 
  mutate_at(vars(starts_with('bpq')),
                 ~case_when(. == 1 ~ 'Never',
                            . == 2 ~ 'Occasionally',
                            . == 3 ~ 'Sometimes',
                            . == 4 ~ 'Usually',
                            . == 5 ~ 'Always'))
```

```{r, error=T, purl=F, warning = F}
BPQ_all_scoring(test_data_character)

```

Observe how the function still runs, and gives an output, but all the subscale scores are NA, and the Percent Missing for each subscale is 100%. 


### Own codes for missing values
Some users code missing values with some value other than NA, such as -99 or 999. This will cause the function output to have incorrect values, and all the percent missing columns to show 0.

First we will simulate this error by creating a new dataframe, test_data_missing, by changing missing values to -99.
```{r}
test_data_missing <- test_data %>% 
  mutate_all(~ifelse(is.na(.), -99, .))

test_data_missing
```


```{r}
BPQ_all_scoring(test_data_missing)
```

Observe the effect on the subscale scores, which should never be negative. Be sure to change all missing values to NA prior to running BPQ_all_scoring.

